### 2020-04-16 dataclean.tex
tweak

As most analysis software uses table-like data, we fill the needed
repeats of values missing in the raw data (see
Fig.~\ref{fig:dataraw}. First, we reduce the data to the GPU that were
removed later than 2013 to focus our analysis epoch on units installed
in the second rework cycle. After this reduction, there were stil six
older units remaining, which we also removed to have a clean third
epoch set of units for the analysis. We do some further processing to
handle time overlaps in a tiny fraction (under 0.0007 in GPU life and
0.0002 in location life) of recorded life in the raw records by simply
dropping the overlapping life times.

>>>>

As most analysis software uses table-like data, we fill the needed
repeats of values missing in the raw data (see
Fig.~\ref{fig:dataraw}). First, we reduce the data to the GPU that
were removed later than 2013 to focus our analysis epoch on units
installed in the second rework cycle or later. After this reduction,
there were stil six older units remaining, which we also removed to
have a clean third epoch set of units for the analysis. We do some
further processing to handle time overlaps in a tiny fraction (under
0.0007 in GPU life and 0.0002 in location life) of recorded life in
the raw records by simply dropping the overlapping life times.
